### 2018-12-05 chapters/2-methods.tex
restructuring postprocess

Ten of the patients were excluded from further analysis due to presence of
motion (n=2), severe susceptibility artifacts (n=5), or incomplete data (n=3).
The characteristics of the remaining 62 patients are shown in Supporting
Material (Table S1). Their median age was 65 years (ranging from 45 to 73
years), while the median serum PSA value was 9.3 ng/ml (ranging 1.3 to 30.0
ng/ml). The number of patients having one, two, and three lesions was 29, 28,
and 5, respectively.

@@

The signal intensity of a T₂w image is not a specific tissue property and
this non-standardness of T₂w images (``intensity drift'') requires
standardization to a common scale. To correct this bias, a histogram alignment
method was used, as described by \citet{Nyul1999,Nyul2000}. This simple method
transforms the images to make their histograms match at certain landmark
locations,  and interpolates the values between. In this study, the deciles
(i.e.\ every tenth percentile) were used as landmarks, as suggested by
\citet{Nyul1999}. Only delineated prostate volume was considered for histogram
averages, as other parts of the image might distort the learning. The result was
validated by visual inspection.

@@

where $S(b)$ is the signal intensity as a function of $b$ value, $S_0$ is the
signal intensity at $b=0$~s/mm², ADCₘ is the apparent diffusion coefficient
of the monoexponential model, ADCₖ is the apparent diffusion coefficient of
the kurtosis model, and K is the kurtosis. The fitting procedure was performed
using the Broyden-Fletcher-Goldfarb-Shanno (BFGS) algorithm \citep{Shanno1985}
implemented by the dlib \citep{King2009} library. In order to find a reliable
fit and prevent local minima, the algorithm was executed with multiple evenly
spaced initialization values. Their intervals (step sizes) were for ADCₘ
0.1--3.0~µm²/ms (0.01~µm²/ms), for ADCₖ 0.01--3.0~µm²/ms (0.1~µm²/ms), and
for K 0.0001--4.0 (0.2).

@@

where $S(\TE)$ is the signal intensity at given time $\TE$, $S_0$ is the signal
intensity at $\TE=0$~ms, and T₂ is the spin-spin relaxation time. The
Levenberg-Marquardt algorithm was used for fitting, as implemented by the SciPy
library, with the multiple initialization values of 0.0~ms to 300~ms with step
size of 50~ms. T₂ relaxation values were constrained to 1--300~ms interval.

>>>>

Ten of the patients were excluded from further analysis due to presence of
motion (n=2), severe susceptibility artifacts (n=5), or incomplete data (n=3).
The characteristics of the remaining 62 patients are shown in Supporting
Material (Table S1). Their median age was 65 years (range 45--73 years), while
the median serum PSA value was 9.3 ng/ml (range 1.3--30.0 ng/ml). The number of
patients having one, two, and three lesions was 29, 28, and 5, respectively.

@@

\subsubsection{T₂w standardization}

The signal intensity of a T₂w image is not a specific tissue property and
this non-standardness of T₂w images (``intensity drift'') requires
standardization to a common scale. To correct this bias, a histogram alignment
method was used, as described by \citet{Nyul1999,Nyul2000}. This simple method
transforms the images to make their histograms match at certain landmark
locations,  and interpolates the values between.

In this study, the deciles (i.e.\ every tenth percentile) were used as
landmarks, as suggested by \citet{Nyul1999}. Only delineated prostate volume was
considered for histogram averages, as other parts of the image might distort the
learning. The result was validated by visual inspection.

\subsubsection{DWI fitting}

@@

where $S(b)$ is the signal intensity as a function of $b$ value, $S_0$ is the
signal intensity at $b=0$~s/mm², ADCₘ is the apparent diffusion coefficient
of the monoexponential model, ADCₖ is the apparent diffusion coefficient of
the kurtosis model, and K is the kurtosis.

The fitting procedure was performed using the Broyden-Fletcher-Goldfarb-Shanno
(BFGS) algorithm \citep{Shanno1985} implemented by the dlib \citep{King2009}
library. In order to find a reliable fit and prevent local minima, the algorithm
was executed with multiple evenly spaced initialization values. Their intervals
(step sizes) were for ADCₘ 0.1--3.0~µm²/ms (0.01~µm²/ms), for ADCₖ
0.01--3.0~µm²/ms (0.1~µm²/ms), and for K 0.0001--4.0 (0.2).

\subsubsection{T₂ fitting}

@@

where $S(\TE)$ is the signal intensity at given time $\TE$, $S_0$ is the signal
intensity at $\TE=0$~ms, and T₂ is the spin-spin relaxation time.

The Levenberg-Marquardt algorithm was used for fitting, as implemented by the
SciPy library, with the multiple initialization values of 0.0~ms to 300~ms with
step size of 50~ms. T₂ relaxation values were constrained to 1--300~ms interval.
